### 2019-07-10 2-Chapters/Conclusion/conclusion.tex
DONE

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% \section{General Conclusion}
\subsection*{General Conclusion}

@@

We started this manuscript by detailing the historical, scientific and technical contexts of our research during this PhD, which studied how decentralized low-cost machine learning technique can be used to automatically improve a certain aspect of wireless telecommunications.
%
We explained the problems that motivate and justify our works.
% and we presented the main contributions produced during the last three years.
%
The main question we studied was \emph{``Can we adapt the decision making tools already successfully applied to Cognitive Radio for Opportunistic Spectrum Access to the specific needs of CR for the (future) Internet of Things networks?''}
%
This PhD manuscript is organized in two parts.
It first focused on giving a strong theoretical background on the reinforcement learning model considered in this thesis, that is the multi-armed bandit model.
The manuscript then focused on our problems of solving the spectrum scarcity issue in unlicensed bands, in the context of the future Internet of Things networks,
and on extending to the specificities of such IoT networks the underlying ideas of previously studied applications of machine learning to solve the spectrum scarcity issue in licensed networks.

@@

>>>>

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% \section{General Conclusion}
% \subsection*{General Conclusion}

@@

We started this manuscript by detailing the historical, scientific and technical contexts of our research during this PhD.
% which studied how decentralized low-cost machine learning technique can be used to automatically improve a certain aspect of wireless telecommunications.
%
We explained the problems that motivate and justify our works.
% and we presented the main contributions produced during the last three years.
%
The main question we studied was \emph{``Can we adapt the decision making tools already successfully applied to Cognitive Radio for Opportunistic Spectrum Access to the specific needs of CR for the (future) Internet of Things networks?''}
%
% This PhD manuscript
% is organized in two parts.
% It
We first gave a strong theoretical background on the reinforcement learning model considered in this thesis, that is the multi-armed bandit model.
We then focused on our problems of solving the spectrum scarcity issue in unlicensed bands, in the context of the future Internet of Things networks,
and on extending to the specificities of such IoT networks the underlying ideas of previously studied applications of machine learning to solve the spectrum scarcity issue in licensed networks.

@@

% \hr{}

% \vfill{}
